\vspace{-0.5in}{\bfseries\scshape Transfer Learning for computationally limited training of Vision Transformers on art classification tasks } \\ \vspace{1ex} \normalsize{Bachelor's Project Thesis}\vspace{-2ex}

### 2022-04-25 writing/tex/draft_introduction.tex
Still have to give it a final read, but seems like my first draft is done now..

It is for this reason the paper that first introduced ViTs \citep{dosovitskiy2020image} mentions using pre-trained models rather than randomly initialised ones, as it allows general knowledge about images to be carried over to the new task. This technique falls within the category of TL, which will be cover below.

@@

Another ``shortcomming'' of \citeauthor{matsoukas2021time} is that it merely examined whether ViTs can use TL to outperform CNNs in a domain that happens to be characterized by limited-sized datasets, but that it did not actively focus on the extent to which ViTs can be made useful in limited data/compute environments. More related to this is \citeauthor{touvron2021training} (\citeyear{touvron2021training}), which proposed transformer-specific distillation-based learning techniques to make ViTs applicable for smaller datasets. This is not necessarily related to TL as defined in this paper, however.
% matsoukas2021time not specifically focussed on seeing to what degree TL allows ViTs to dominate CNNs in limited compute/data environments
\\\\
The current study limits itself to the task of identifying which materials were used in artistic content. For this, it will examine to what extent TL techniques (both fine-tuning and OTS) allow ViTs to become the preferred architecture when compute resources are limited, and attempt to find a methodology that is preferred in circumstances as described. It will do this by means of several experiments, and both qualitative and quantitative analysis of the results.

>>>>

It is for this reason the paper that first introduced ViTs \citep{dosovitskiy2020image} mentions using pre-trained models rather than randomly initialised ones, as it allows general knowledge about images to be carried over to the new task. This technique falls within the category of TL, which will be covered next.

@@

Another ``shortcomming'' of \citeauthor{matsoukas2021time} is that it merely examined whether ViTs can use TL to outperform CNNs in a domain that happens to be characterized by limited-sized datasets, but that it did not actively focus on the extent to which ViTs can be made useful in limited data/compute environments. More related to this is \citeauthor{touvron2021training} (\citeyear{touvron2021training}), which proposed transformer-specific distillation-based learning techniques to make ViTs applicable for smaller datasets. This is not necessarily related to TL as defined in this paper, however.
% matsoukas2021time not specifically focussed on seeing to what degree TL allows ViTs to dominate CNNs in limited compute/data environments
\\\\
The current study will examine to what extent TL techniques (both fine-tuning and OTS) allow ViTs to become the preferred architecture when compute resources are limited, and attempt to find a methodology that is recommended in these circumstances. It will, however, restrict itself to a single CV task, namely material classification of artworks. Several experiments will be performed, of which results will be analysed both quantitatively as well as qualitatively.

%The current study limits itself to the task of identifying which materials were used in artworks. For this, it will examine to what extent TL techniques (both fine-tuning and OTS) allow ViTs to become the preferred architecture when compute resources are limited, and attempt to find a methodology that is preferred in circumstances as described. It will do this by means of several experiments, and both quantitative and qualitative analysis of the results.

More formally, the following research question is proposed: \quote{\textit{To what extent (and in what manners) does utilizing TL allow ViTs to perform on par with CNNs for material classification of artworks, when compute resources are limited to a single GPU/TPU?}}
